---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(tidyverse)
```

# fakecountry

> A completely made up country consisting of smaller geographical areas to illustrate spatial statistical methods. Because... why not?

<!-- badges: start -->
<!-- badges: end -->


This is what I did:

1. Create a set of random points that will serve as the centroids for the areas.
2. Create a [Voronoi Diagram](https://en.wikipedia.org/wiki/Voronoi_diagram) to create polygons based on these points.
3. Limit the Voronoi diagram to a bounding box to represent the country's borders. I used an irregular pentagon for this purpose, to make it more natural looking.
4. Look out for very small slivers of areas which are not very realistic. Any areas with measure less than a threshold are excluded.
5. Save the polygons to a shapefile (in the data folder).

The actual script to generate the fake country is in Python. 
To load it in R, do the following.

```{r}
library(sf)
fakecountry <- read_sf("data/fakecountry/", quiet = TRUE)
fakecountry
```

## Plot

```{r, eval = -1}
library(tidyverse)
ggplot(fakecountry) +
  geom_sf(aes(fill = id)) +
  scale_fill_viridis_c(option = "turbo") +
  theme_bw() +
  theme(legend.position = "none") +
  labs(title = "My fake country",
       subtitle = "Ready for analysis!")
```
